Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-19 ms.tex
minor wording changes

\title{Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
\textcolor{red}{Thing to try: did I try a circular aperture centered on the knot? try to use centroid from SW to adjust the position of the source extraction box}
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure*}
\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
The crosshatch pattern is also 
The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
}\label{fig:otisLWflatVsNoFlat}
\end{figure*}

>>>>

\title{Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors}

@@

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{tser_LWSW_OTIS.pdf}{0.6\textwidth}{Grism Time Series}}
\caption{Time series of the simultaneous SW/LW Time Series Stability test
}\label{fig:otisLWSWtser}
\end{figure*}

@@

\begin{figure*}
\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
There are small offsets in the flux os the spectrum also because of the flat field.
}\label{fig:otisLWflatVsNoFlat}
\end{figure*}
